The value of intermediation

### 2022-09-13 src/presentation/presentation.qmd
Add notes to most slides

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

::: {.column .fragment width="5%"}
:::

@@

@@

@@

>>>>

::: {.notes}
 - Just the intuition in a few words
:::

@@

::: {.notes}
 - Two ingredients: players (left) and characteristic function (right)
 - We don't care about strategies, only about value achieved by coalitions
:::

@@

::: {.notes}
 - Most direct definition of Shapley value
 - Closed-form expression
 - Generally computationally expensive, but not in this case
:::

@@

::: {.notes}
 - You don't need to think about cooperative game theory in the following part
 - Think of it as a convenient gain sharing rule with some (cooperative and non-cooperative) microfoundations
:::

@@

::: {.notes}
 - Very simple setting
 - Conveys the intuition behind the results
:::

@@

::: {.notes}
 - Not only platforms. Also describes
   - upstream-downstream setups
   - generally any setting with an important large palyers and many identical small ones
:::

@@

::: {.notes}
 - Think of the previous figure with the orderings
 - Main insight: each ordering with the platform at position $k$ has the same probability
:::

@@

::: {.notes}
 - The bargaining problem is reduced to a simple integral
:::

@@

::: {.notes}
 - The comparative statics seem to coincide with one's intuition about bargaining
:::

@@

::: {.notes}
 - Skippable if don't have time
:::

@@

::: {.column width="5%"}
:::

@@

::: {.notes}
 - Intentionally simple model
 - Most elemnts borrowed from [@anderson2021hybrid]
:::

@@

::: {.notes}
My contributions
 - Shapley-value is a good fit for platform settings
 - The continuous case is vary tractable in this speciific setting
 - Results about the weighted value are mine
 - Insight that hybrid platforms have higher bargaining power, leading to more distortion
:::

@@

::: {.notes}
 - Some extensions are straightforward
 - However, some situations just don't fit the model
 - Essentially a plug-and-play approach when one some middle ground between one side taking all the gains
:::
